Leaf traits drive differences in biomass partitioning among major plant functional types

### 2015-01-14 manuscript.Rnw
Deleted functions-ms.R; no longer needed
All log axes are formatted consistently. Closes #3

<<preload, echo=FALSE>>=
library(knitr)
opts_chunk$set(echo=FALSE)
source("R/functions-ms.R")
baad <- readRDS("downloads/baad.rds")
@

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{FigureS5.pdf}
    \caption{\textbf{Plant functional types diverge strongly in mass-based partitioning, but converge in area-based partitioning.} Shown are histograms of leaf mass per area (an index of leaf construction cost) ($M_F/A_F$), leaf mass per unit basal stem area ($M_F/A_S$) and leaf area per unit basal stem area ($A_F/M_S$) grouped by the three major plant functional types. Arrows indicate means (same as in Fig.~\ref{fig:figure2}).}
    \label{fig:figures5}
\end{figure}

>>>>

<<preload, echo=FALSE>>=
library(knitr)
opts_chunk$set(echo=FALSE)
baad <- readRDS("downloads/baad.rds")
@

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{FigureS5.pdf}
    \caption{\textbf{Plant functional types diverge strongly in mass-based partitioning, but converge in area-based partitioning.} Shown are histograms (as probability density functions) of leaf mass per area (an index of leaf construction cost) ($M_F/A_F$), leaf mass per unit basal stem area ($M_F/A_S$) and leaf area per unit basal stem area ($A_F/M_S$) grouped by the three major plant functional types. Arrows indicate means (same as in Fig.~\ref{fig:figure2}).}
    \label{fig:figures5}
\end{figure}
